Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

Surface liquid water is the definition of planetary habitability: water is required for life as we know it, and life will only be detectable on an exoplanet if it is present at the surface. Hence the search for life on exoplanets typically focuses on habitable planets. To first order, the presence of surface liquid water can be predicted by the flux it receives from its star. The habitable zone (HZ) describes the range of semi-major axes for which an Earth twin could maintain surface liquid water around a given main sequence star \citep{kasting93}.  The HZ is convenient because a planet can be deemed habitable based on solely on its orbital separation, but it remains an untested hypothesis. Ideally, we will empirically establish the presence of liquid water on an exoplanet before trying to interpret its putative biosignatures.

>>>>

Surface liquid water is the definition of planetary habitability: water is required for life as we know it, and life will only be detectable on an exoplanet if it is present at the surface. Hence the search for life on exoplanets typically focuses on habitable planets. To first order, the presence of surface liquid water can be predicted by the flux it receives from its star. The habitable zone (HZ) describes the range of semi-major axes around a given main sequence star for which an Earth twin could maintain surface liquid water \citep{kasting93}.  The HZ is convenient because a planet can be deemed habitable based on solely on its orbital separation, but it remains an untested hypothesis. Ideally, we will empirically establish the presence of liquid water on an exoplanet before trying to interpret its putative biosignatures.
